\vfill A Testing Framework for Web Application

### 2014-01-31 Paper/paper.tex
Client/Server fixing and additions

\subsubsection{What is the Client-side Portion?}
\todo{Redo this paragraph...}
The simple answer is: You. Your phone, computer, tablet, or other device communicating with a given website or application is the client. More specifically, the browser or service you're using to communicate with the web is the client. The client is responsible for requesting assets and then displaying them in a human-readable way. It is the client that controls the capabilities and user interface of the web application.

\subsubsection{What is the Server-side Portion?}
\todo{Redo this paragraph...}
A server is the entity, be it machine, person, or cloud service, that stores the information about a given web page or application. The server stores all assets, HTML pages, images, videos, databases, etc, and provides them upon request to the client. The server's job is to ``serve'' assets, be them web pages or images, to a client that is requesting them.

\subsubsection{Client and Server Interactions}
The client has limited access to resources on any given web application. This access is restricted by the server. Without such restrictions in place, someone could access user databases, credit card information, order reports, etc. In addition, there would be an overwhelming amount of content for a client to parse through, even if they have no malicious intent.

>>>>

\subsubsection{What is the Client-side Portion?}
First, I'll address what a client is. The simple answer is: You. Your phone, computer, tablet, or other device communicating with a given website or application is the client. More specifically, the browser or service you're using to communicate with the web is the client. 
So now that the client has been clarified, what is the client-side portion of an application? The client-side portion interacts with the browser to request assets from the server and then displaying them in a human-readable way. The client-side also deals with the user interface and interactivity of a web page, e.g., the client-side displays a web form, the client fills in the information and clicks ``submit'' and the client-side packages up the data and sends it to the server-side.
Client-side programming is done in a language that the browser understands, most frequently Javascript. Though not technically programming languages, client-side programming is also done through HTML and CSS which control the look and feel of web pages.

\subsubsection{What is the Server-side Portion?}
Once again, I'll outline a server and then delve into server-side programming. A server is the entity, be it machine, person, or cloud service, that stores the information about a given web page or application. The server stores all assets, HTML pages, images, videos, databases, etc, and provides them upon request to the client. The server also handles all of the processing for interactivity, accounts, and a general number-crunching.
The server-side portion of an application, then, stores all of the assets, accounts, and structure of the entire application. The server-side authenticates users, retrieves data from databases, processes large data, and send information, be it assets or results, back to the client to display to the user.

\subsubsection{Client and Server Interactions}
The client has limited access to resources on any given web application. This access is restricted by the server. Without such restrictions in place, someone could access user databases, credit card information, order reports, etc. In addition, there would be an overwhelming amount of content for a client to parse through, even if they have no malicious intent.
Clients communicate with the Server through a request-response architecture. Clients send a request to the server, sometimes with information attached, such as a form submittal or login, and the server returns a response with either a success/failure message, or additional data.
